Childhood exposure to non-persistent endocrine disruptors, glucocorticosteroids, and attentional function: A study based on the parametric g-formula

### 2024-03-18 output/paper/manuscript.qmd
Compiled manuscript.

format:
  html: default
  docx:
    # reference-doc: reference_document.docx
    page-width: 8.3
    citeproc: true
    mermaid:
      theme: neutral
  pdf:
    documentclass: article
    geometry:
      - top=30mm
      - left=20mm
      - heightrounded
    pdf-engine: lualatex
    number-sections: true
    toc: false
    keep-tex: false
    include-in-header:
      text: |
        \usepackage{lineno}
        \usepackage{rotating}
        \usepackage{float}
        \usepackage{typearea}
    include-before-body:
      text: |
        \linenumbers

>>>>

format:
  html:
    embed-resources: true
  docx:
    # reference-doc: reference_document.docx
    page-width: 8.3
    citeproc: true
    mermaid:
      theme: neutral
  pdf:
    documentclass: article
    geometry:
      - top=30mm
      - left=20mm
      - heightrounded
    pdf-engine: lualatex
    number-sections: true
    toc: false
    keep-tex: false
    include-in-header:
      text: |
        \usepackage{lineno}
        \usepackage{rotating}
        \usepackage{float}
        \usepackage{typearea}
    include-before-body:
      text: |
        \linenumbers
